Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-18 prop_letter.tex
prop_letter.tex \section{Intervals of Uncertainty} Quantum Expectation Value updated...

After we defined QIVPM, we can merge the definition of quantum expectation
value~(\ref{eq:quantum-expectation}) and the classical Choquet integral~(\ref{eq:interval-expectation})
to the following definition.

>>>>

After we defined QIVPMs, we can easily define the expectation value
of an observable with respect to a QIVPM by adopting the idea of the
classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
the expectation value of $X$ with respect to a probability measure~$\mu$
is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
Since the definition of Choquet integral is just using a more complex
but reasonable way to compute the weight, we can apply the same algorithm
on an observable and get the following definition.
